\documentclass[a4, 10pt]{article}
        \usepackage{geometry}
                \geometry{
                        a4paper,
                        total={210mm,297mm},
                        tmargin = 19.8mm,
                        bmargin = 19.8mm,
                        lmargin = 17.4mm,
                        rmargin = 17.4mm,
                }

        \usepackage{titlesec}
                \titleformat{\section}
                        {\normalfont\fontsize{12}{8}\bfseries}{\thesection}{0.5em}{}
                        [{\titlerule[0.5pt]}]
                \titleformat{\subsection}
                        {\normalfont\fontsize{10}{6}\bfseries}{\thesubsection}{1em}{}

        \setlength{\parindent}{0pt}
        \renewcommand{\baselinestretch}{0}
        \usepackage{setspace}

        \newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
                \setcounter{tocdepth}{5}
                \setcounter{secnumdepth}{5}


% START
\begin{document}

        \title{
                \HRule{0.5pt}
                \HRule{0.5pt}\\ [0.45cm]
                \center{\textsc{Lewis Britton}}\\
                \center{\textsc{University of Strathclyde}}\\ [0.5cm]
                \HRule{0.5pt}
                \HRule{0.5pt}
                }
        \date{}
        \maketitle

\setstretch{1.0}{

\begin{center}
\begin{tabular}{ l l }
        \textbf{Mail To:} wi.lbritton@yahoo.com & \textbf{Telephone:} 07415 212 056\\ 
        \textbf{Website:} http://lewisbritton.com/ & \textbf{GitHub:} https://github.com/FedeRog1977   
\end{tabular}
\end{center}

}


% BASICALLY A GLOBAL STRETCH
\setstretch{1.25}{


% OBJECTIVES
\section{Objective \& Preliminaries}

\begin{itemize}
\setlength\itemsep{0cm}
        \item Primary goal is to translate my efficiency, pragmatics and logic into the most optimal and suitable client satisfaction. 
	\item I seek a role which is suited to my interests, skillset and motivational drivers. This role satisfies those criteria. Therefore, work standard will reflect this. 
	\item I aim to remain in the Glasgow area for the forseeable future to concentrate focus. This role is appropriate to that standard.
\end{itemize}


% WHY BARCLAYS
\section{What I Will Offer}

\subsection{Barclays Specific}

I am a fan of the Barclays name. The Barclays cultural and societal inclusion system is straight-to-the-point with minimal bloat. I respect the system. Specifically, I take great interest in wealth management. My respect for and practice with accuracy and logic perfectly matches the punctual nature of combining necessary communication mehtods with comma-separated value environment management. As has been displayed through previous employment, my communication, literacy, accent, verbal respect, interpretation, understanding, empathy, care and delivery is of high-standard and in favour of clients. Request reference, if required.\\

Regarding remote communication, I am familiar with various CSV environments, primarily SC-IM and Microsoft Excel. I communicate logically and pragmatically with the correct amount of empathy, tone and emotion. I am familiar with more efficeint methods of electronic mail and telecommunication,  for example through my mail client: mutt and, though my Cisco CP-7962G. Having managed my own `wealth', investments and cash flows extremely efficiently for five years now, I have the skill it takes to translate my results to clients. My efficiency and decision making is in favour of sustainable growth, in respect of the client and myself.

\subsection{Additional}

I have the ability to adapt and change to suit new and developing situations and tasks which will allow a consistent flow in operations. Showing my determination and stamina through new opportunities, relations and experiences to adopt new skills and knowledge is an important part of service to me also. Which all would enhance the client’s experience. I find it thrilling to set and also attain high goals and expectations and respond to pressure due to my competitive and punctual nature. This further motivates me to put across my efficient and logical structure to create systems of efficiency.\\

Teamwork is equally as important to me as self-management and leadership and I believe that I make an excellent listener and learner. And most importantly of all to me, is integrity. Good service is not fulfilled without honesty, respect, trust and loyalty. Which are all attributes I believe I take pride in owning. I would always use this to provide the best service I possibly could.

}

% Additional (Grain & Grind)

% Objective 

% I am currently in my further year of study at university so I am seeking a part-time job of anywhere between 10 and 16 hours per week ideally. Of course, this is subject to your requirements. My goal with this role is to give great pleasure to the people of my home village of Giffnock by fulfilling their caffeine requirements while exercising one of my greatest passions. I also believe that working a part-time job such as this alongside university work leads to improved efficiency, momentum and drive in both areas. 

% Why Grain & Grind

% I have been a fan of the Grain & Grind brand since I made the life-changing decision this year to purchase a new Bialetti Preziosa French Press to accompany my matching Venus Moka Pot. I tailored my coffee shelf to contain only the best beans to compliment the best equipment. On that shelf of course was a selection of your Brazilian Santos and Bungo Roast, with which I fell in love immediately. So forth, it would of course be a pleasure to work in the surroundings of what I believe to be such a high quality product and share this with people in my local.

% 'What I Will Offer' Seciton

% It’s important to me that I create a positive image quickly as I believe this will reflect extremely well in the productive position in a high-quality, high-energy nature you offer and display in your coffee and barista service. I am well presented and extremely polite which will project a positive image of myself and the business. My friendly but efficient nature along with an accurate, detailed and careful work ethic in any task will aid this by providing a satisfying service for the customer and a pleasant environment between myself and my colleagues. 

% I also have the ability to adapt and change to suit new and developing situations and tasks which will allow a consistent flow in operations. Showing my determination and stamina through new opportunities, relations and experiences to adopt new skills and knowledge is an important part of service to me also. Which all would enhance the customer’s experience. I find it thrilling to set and also attain high goals and expectations and respond to pressure due to my competitive and punctual nature. This further motivates me to put across my efficient and logical structure to create systems of efficiency.

% Teamwork is equally as important to me as self-management and leadership and I believe that I make an excellent listener and learner. And most importantly of all to me, is integrity. Good service is not fulfilled without honesty, respect, trust and loyalty. Which are all attributes I believe I take pride in owning. I would always use this to provide the best service I possibly could.

\end{document}
