\documentclass[11pt, english]{article}
        \usepackage{geometry}
                \geometry{
                        a4paper,
                        total={210mm,297mm},
                        tmargin = 19.8mm,
                        bmargin = 19.8mm,
                        lmargin = 17.4mm,
                        rmargin = 17.4mm,
                }

	\usepackage[utf8]{inputenc}
	\usepackage[T1]{fontenc}
        \usepackage{ebgaramond}

        \usepackage{titlesec}
                \titleformat{\section}
                        {\normalfont\fontsize{12}{8}\bfseries}{}{0.5em}{}
                        [{\titlerule[0.5pt]}]
                \titleformat{\subsection}
                        {\normalfont\fontsize{10}{6}\bfseries}{}{1em}{}

        \setlength{\parindent}{0pt}
        \renewcommand{\baselinestretch}{0}
        \usepackage{setspace}

        \newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
                \setcounter{tocdepth}{5}
                \setcounter{secnumdepth}{5}

	\usepackage{hyperref}
                \hypersetup{
                        colorlinks=true,
                        linkcolor=black,
                        filecolor=magenta,
                        urlcolor=cyan,
                }

\begin{document}

\pagenumbering{Roman}

        \title{
                \HRule{0.5pt}
                \HRule{0.5pt}\\ [0.45cm]
                \center{\huge\textsc{Lewis Britton}}\\
		\center{\Large\textit{The }\textsc{University of Strathclyde}}\\ [0.5cm]
                \HRule{0.5pt}
		\HRule{0.5pt}\\ [-0.45cm]
                }
        \date{}
        \maketitle

\setstretch{1.0}{
   
\begin{center}
\begin{tabular}{r|l}
        \textbf{Mail To:} wi.lbritton@yahoo.com & \textbf{Telephone:} 07415 212 056\\ 
        \textbf{Website:} \href{http://lewisbritton.com}{lewisbritton.com} & \textbf{GitHub:} \href{https://github.com/FedeRog1977}{FedeRog1977}
\end{tabular}
\end{center}

}

\setstretch{1.25}{


\section{Objective \& Preliminaries}

\begin{itemize}
\setlength\itemsep{0cm}
	\item Be proud to work for a Giffnock business local to myself, which I very much respect and enjoy. 
	\item To be part of the homely Ca Va and Giffnock business community.
	\item Translate my need for an extremely efficient and clean lifestye into an equally efficient workplace, showing respect for the highly-valued, desirable and fast-paced Ca Va service environment.
	\item Reflect my significant interests in formal-casual dining, drinking, excellent customer service and high quality in a way which highlights all of these respective aspects also seen in Ca Va.
\end{itemize}


\section{What I Will Offer}

\subsection{Ca Va Specific}

As I mention, I have been a fan of the Ca Va establishment since the very first day of Cherry Tree. It even broke my loyalty to the OP! I guess that's what a higher quality of service and product does. I enjoy the versatility of Ca Va in its ability to be an excellent breakfast and afternoon coffee location, to its transformation to a stunning evening venue. I would indeed love to be on the service end of this; observing and fulfilling the needs of the clientele. It's a process I would excel within due to my ability to observe and produce the correct relevant service at varying times.\\

The kitchen porter role does of course suit my abilities very well. Although I have not completed a role as such previously, my day-to-day personality and idiosyncrasies require me to be a very pragmatic, logical, clean and efficient person; wasting the least amount of time possible. I have of course had my share of service experience, working in retail and supermarket environments previously. My communication is sound; with care for no workplace `messing around', as they say. This is really only something you can see in person but, there's no place for wasting time.

\subsection{Additional}

I have the ability to adapt and change to suit new and developing situations and tasks which will allow a consistent flow in operations. Showing my determination and stamina through new opportunities, relations and experiences to adopt new skills and knowledge is an important part of service to me also. Which all would enhance the client’s experience and efficiency of the workplace. I find it thrilling to set and also attain high goals and expectations, and respond to pressure due to my competitive and punctual nature. This further motivates me to put across my efficient and logical structure to create systems of efficiency.\\

Teamwork is equally as important to me as self-management and leadership and I believe that I make an excellent listener and learner. And most importantly of all to me, is integrity. Good service is not fulfilled without honesty, respect, trust and loyalty. Which are all attributes I believe I take pride in owning. I would always use this to provide the best service I possibly could.

}

\end{document}
